Constructing the transition graphs of interacting hysterons

### 2022-06-29 Paper_draft.tex
Started work on base graph argument

We now describe two considerations that decrease the number of unique transition graphs, namely the 

@@

A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed. Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$. We base our method on the design inequalities, as introduced in Section \ref{ssec:ordering} and elaborated on in the Supplemental Information. We use the design inequalities to argue that the transitions that make up a graph, whether they are single flips or avalanches, can only be constructed out of a set collection of elementary steps. We use our method to construct a list of candidate graphs, then filter out the realizable graphs by explicitly checking the solution space of the design inequalities.\\

@@

>>>>

We now describe two considerations that decrease the number of unique transition graphs, namely exchange symmetry and the existence of Garden-of-Eden states. 

@@

A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed. Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$. We base our method on the design inequalities, as introduced in Section \ref{ssec:ordering} and elaborated on in the Supplemental Information. We use the design inequalities to argue that the transitions that make up a graph, whether they are single flips or avalanches, can only be constructed out of a fixed collection of elementary steps. We use our method to construct a list of candidate graphs, then filter out the realizable graphs by explicitly checking the solution space of the design inequalities.\\

@@

\subsection{Base graphs}
We now argue, based on the design inequalities, how avalanches must be constructed from a fixed choice of elementary steps.\\
For the hysteron $i$ to flip up from the state $S$, the up switching field of hysteron $i$ must be the lowest of all the hysterons:
\begin{equation}\label{eq:initial_transition}
U_i^+(S) = \min_{s_j=0} U_j^+(S)
Now suppose that the state $S$ is not stable, but is instead a part of an avalanche. Let $U*$ be the field at which the avalanche is initiated. Hysteron $i$ must then have
\begin{equation}\label{eq:avalanche_unstable}
U_i^+(S) \leq U*
while all other hysterons $j$ with the state $s_j = 0$ must be stable, and therefore have
\begin{equation}\label{eq:avalanche_stable}
U_j^+(S) > U*
Combining equations \ref{eq:avalanche_unstable} and \ref{eq:avalanche_stable}, we find that Equation \ref{eq:initial_transition} is implied.\\
